MSc Project - Modelling a Double-Barred Galaxy as a Double Binary

### 2017-08-14 workspace/DoubleBars/MScProjectDoubleBarsv2.tex
writeup!

For a four body problem Equation 1 results in the following:

@@

>>>>

For a four body problem 
this equation results in the following:

@@

\subsection{Compilers}
As I had converted OdeInt into Fortran 90 I wanted to make sure I hadn't introduced any errors. I therefore compared the output of the Numerical Recipes
version of OdeInt with mine. I was compiling with GFortran and the Fortran 77 version was compiled with g77. They were different! So naturally concerned 
I then compiled the Fortran 77 version with GFortran. The results were identical to mine, which satisified me that I hadn't introduced any errors.
